Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{ccccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{5-7}
              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

>>>>

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{ccccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{5-7}
              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
            \hline
            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

We observe significant dWER increasing without concatenating the reference audio to the mixture, 
as shown 
the TSELM-S-NoConcat in Table \ref{main_exp}. WavLM \cite{wavlm} is demonstrated to have target speaker 
separation capability. The input audio should have the mixture less than 50\% and have the first utterance as target speaker. The output will be a coarse denoised audio emphasizing the target speaker. 
If the whole input is mixture, we have found that WavLM sometimes will 
extract the wrong speaker. Our current pipeline focuses on the separation strategy
